Trajectory model of passive kelp dispersal

### 2020-07-07 thesis_chapter_3.Rmd
Added to introduction

Methods used in the field of chemical engineering provide an alternative approach to estimating drag of macroalgae by means of formulae to calculate drag based on shape.

@@

>>>>

Methods used in the field of chemical engineering provide an alternative approach to estimating drag of macroalgae by means of formulae to calculate drag based on shape. Chemical engineers in the field of fluid dynamics which come across similar problems when including drag use an approach known as a 'spherecity factor'. A spherecity factor is the ratio of the surface area of a sphere having the volume as the irregular shaped particle (s) to the actualo surface area of the particle (s_d) such that $$\psi=s/s_d$$. The values are dependent on the shape of the object and a range of values have been determined based on numerous experimental work. A table of various shapes and the associated spherecity factor is provided in the appendix.

@@

# Appendix

Insert table of spherecity factors.
